Summer 2024 Report

### 2024-12-12 Relations/Report.tex
Minor tidying

\newpage
\section{Counterexamples}
The following counterexamples are used to rule out certain implications between properties from holding.
\sacomment{How should we present this section. Is it enough to have diagrams and a list of what they are a counter to?}
\subsection*{Counterexample 1}
\begin{center}

@@

\end{center}
Counterexample to:
\begin{itemize}
  \item WCR $\implies$ CR
  \item WCR  $\implies$ WNFP
  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ R a c $\to$ (R *) c b }
  \item WCR and WN $\implies$ CR
  \item WCR and WN $\implies$ SN
  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP) in the report}
\end{itemize}

@@

  \textcolor{red}{SA: The above is a bit messy, can we make it cleaner?}
  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$

>>>>

\newpage
\section{Counterexamples}
The following counterexamples are used to rule out certain implications between properties from holding.
\subsection*{Counterexample 1}
\begin{center}

@@

\end{center}
Counterexample to:
\begin{itemize}
  \item WCR $\implies$ CR
  \item WCR  $\implies$ WNFP
  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ R a c $\to$ (R *) c b }
  \item WCR and WN $\implies$ CR
  \item WCR and WN $\implies$ SN
  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define IOW in the report}
\end{itemize}

@@

  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
